Analysis of Climate Sensitivity using HadAM3

### 2014-04-18 article.tex
Add in a propert (read from .bib files) bibliography/ref section.
Add in a handy little tool for gen/view/cleaning up latex files.

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}

@@

%\bibliographystyle{agufull08}
%\bibliography{sample-bib-08}
\begin{thebibliography}{2}
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{\textit{Brown}(1967)}]{bro1967}
Brown, R. J.~E. (1967), Permafrost in {Canada}, \textit{Map 1246A}, Geol. Surv.
  of Can., Ottawa, Ont.

\bibitem[{\textit{Englemann et~al.}(1986)\textit{Englemann, Perkins, Hagan, and
  Haller}}]{Englemann1986}
Englemann, R.~J., R.~W. Perkins, D.~I. Hagan, and W.~A. Haller (1986), Washout
  coefficients for selected gases and particulates, paper presented at 59th
  Annual Meeting, Air Pollut. Control Agency, San Francisco, Calif., 20--24
  June.

\end{thebibliography}

>>>>

% Does not apply to me as I'll just be handing in the PDF.
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}

@@

% BIB_RM
\bibliographystyle{agufull08}
\bibliography{sample-bib-08}
% END_BIB_RM

% BIB_POS

%\begin{thebibliography}{2}
%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%
%\bibitem[{\textit{Brown}(1967)}]{bro1967}
%Brown, R. J.~E. (1967), Permafrost in {Canada}, \textit{Map 1246A}, Geol. Surv.
%  of Can., Ottawa, Ont.
%
%\bibitem[{\textit{Englemann et~al.}(1986)\textit{Englemann, Perkins, Hagan, and
%  Haller}}]{Englemann1986}
%Englemann, R.~J., R.~W. Perkins, D.~I. Hagan, and W.~A. Haller (1986), Washout
%  coefficients for selected gases and particulates, paper presented at 59th
%  Annual Meeting, Air Pollut. Control Agency, San Francisco, Calif., 20--24
%  June.
%
%\end{thebibliography}
